Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-08-07 doc/paper-lcr.tex
more writeup

Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halo, 
and will likely not have access to their spectroscopic redshift either. Instead these properties must be inferred from astrophysical
observables. In principle the only observables are astrometric positions, photometric colours and possibly spectra. In this section we
quantify the errors induced by inferring the halo mass and redshift from the observables. Much work has already focused on using
photometric colours to infer stellar mass \citep[\eg][]{augerstellarpops} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
of $\kappax$. We will investigate three main sources of error: inferring halo mass given observed stellar mass; halos at the wrong redshift
due to photometric redshift error, and; the combination of both redshift and stellar mass errors.

>>>>

Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halo, 
and will likely not have access to their spectroscopic redshift either. Instead these properties must be inferred from astrophysical
observables. In principle the only observables are astrometric positions, photometric colours and possibly spectra. In this section we
quantify the errors induced by inferring the halo mass and redshift from the observables. Much work has already focused on using
photometric colours to infer stellar mass \citep[\eg][]{xxx} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
of $\kappax$. We will investigate three main sources of error: inferring halo mass given observed stellar mass; halos at the wrong redshift
due to photometric redshift error, and; the combination of both redshift and stellar mass errors.

We generate a stellar mass for each halo according to the stellar mass-halo mass relation of \citet{behroozi2010}. From this stellar mass we simulate 
an observed stellar mass by drawing a stellar mass from $\pr(M*_{\mathrm {obs}}|M*_{\mathrm {true}})$. We draw our samples from $\pr(\log(M*_{\mathrm {obs}})|\log(M*_{\mathrm {true}}))$ is given by the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and a Gaussian of width $\sigma_{M*}$ centred on $\log(M*_{\mathrm {true}})$. Where a spectroscopic redshift exists stellar masses can be estimated with a typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large; we use $\sigma_{M*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M*}=0.45$ otherwise. The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
\be
\label{eq:GSMF}
{\dee N \over \dee M*} \propto \left(10^{(M*-M_0(z))}\right)^(1+\alpha(z))) \exp \left(-(10^(M*-M_0(z)))\right)
\ee 
where $M_0(z)=11.16+0.17*z-0.07*z**2$ and $\alpha(z)=-1.18-0.082*z$.
